A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-02-26 manuscript/manuscript.qmd
added RJG as co-author
minor edits to author list and affiliations

**Authors**: Janick Weberpals^1^, Kenneth L. Kehl^2^, Donna R. Rivera^3^, Pallavi Mishra-Kalyani^3^, Georg Hahn^1^, Priyanka Anand^1^, Yanina Natanzon^4^, Janet Espirito^5^, Nicholas J Robert^5^, Andrew J. Belli^6^, Ching-Kun Wang^6^, Sebastian Schneeweiss^1^, Shirley V. Wang^1^

@@

^5^ Ontada, Boston, MA, USA

^6^ COTA, Inc., New York, NY, USA

>>>>

**Authors**: Janick Weberpals^1^, Kenneth L. Kehl^2^, Donna R. Rivera^3^, Pallavi Mishra-Kalyani^3^, Georg Hahn^1^, Priyanka Anand^1^, Yanina Natanzon^4^, Andrew J. Belli^5^, Ching-Kun Wang^5^, Jenna Collins^6^**,** JonathanKish^6^**,** Janet Espirito^7^, Nicholas J Robert^7^, Robert J. Glynn^1^ ,Sebastian Schneeweiss^1^, Shirley V. Wang^1^

@@

^5^ COTA, Inc., New York, NY, USA

^6^ Flatiron Health, Inc., New York, NY, USA

^7^ Ontada, Boston, MA, USA
